Article data analysis

### 2018-10-25 notebooks/article_notebook.Rmd
added MLST plot and test stats

>>>>

## Sequence types per resistance category
```{r}
ST_MIC <- mic_data %>%
  left_join(mlst_data[c("id","ST")], by = "id") %>%
  mutate(SMX_R = ifelse(as.numeric(SMX) > 64, 1, 0),
         TMP_R = ifelse(as.numeric(TMP) > 2, 1, 0),
         CIP_R = ifelse(as.numeric(CIP) > 0.06, 1, 0),
         TET_R = ifelse(as.numeric(TET) > 8, 1, 0),
         NAL_R = ifelse(as.numeric(NAL) > 16, 1, 0),
         CTX_R = ifelse(as.numeric(CTX) > 0.25, 1, 0),
         CHL_R = ifelse(as.numeric(CHL) > 16, 1, 0),
         AMP_R = ifelse(as.numeric(AMP) > 8, 1, 0),
         GEN_R = ifelse(as.numeric(GEN) > 2, 1, 0)) %>%
  mutate(NAL_CIP_R = rowSums(.[,c(15,17)]),
         antres = rowSums(.[,13:21])-NAL_CIP_R) %>%
  select(-c(NAL_CIP_R,SMX,TMP,CIP,TET,NAL,CTX,CHL,AMP,GEN)) %>%
  left_join(isolate_data[c("id", "species")], by = "id") %>%
  gather(AB, res, -c(id, antres, ST, species)) %>%
  group_by(AB, ST, res, species) %>%
  count() %>%
  spread(res, n, fill = 0) %>%
  rename("res" = "1",
         "nonres" = "0") %>%
  group_by(AB, ST) %>%
  mutate(p = res/(res+nonres)*100) %>%
  ungroup() %>%
  mutate(AB = gsub("_R", "", AB))

ggplot(ST_MIC, aes(reorder(ST, p), reorder(AB, -p), fill = p))+
  geom_tile()+
  scale_fill_viridis(guide = guide_colorbar(barheight = 5,
                                            barwidth = 0.5,
                                            label.position = "left",
                                            label.hjust = 0.5,
                                            label.vjust = 0.3,
                                            ticks = TRUE))+
  labs(y = "Antimicrobials")+
  theme(axis.text.y = element_text(size = 4),
        axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.4, size = 8),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size = 10),
        legend.position = "left",
        legend.title = element_blank(),
        legend.text = element_text(size = 7))+
  facet_wrap(~ species, scales = "free_x", ncol = 1)
```

# Statistics
## Grouping of MIC values
```{r}
stat_MIC <- mic_data[c("id", "CIP")] %>%
  left_join(total_df, by = "id") %>%
  left_join(cols_to_add, by = "id") %>%
  select(-c(gyrA, gyrB, parC, parE)) %>%
  mutate(category = ifelse(as.numeric(CIP) > 0.25, 1, 0)) %>%
  select(-c(id, CIP))

test <- glm(factor(category) ~ ., data = stat_MIC, family = "binomial")

summary(test)
plot(test)
```
